Report

### 2020-11-09 report.Rmd
Begin to concatenate analysis + few new plot

pred_log_bm_quad2_plot <- map2(model_log_bm$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
```

>>>>

pred_log_bm_quad2_plot <- map2(model_log_bm$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
legend_quad2 <- get_legend(pred_log_bm_quad2_plot[[1]])
pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
plot_grid(top, legend_quad2, rel_widths = c(1, .1))
```
-

## Link biomass dynamic and environment

```{r}
myload(habitat_press, habitat_pressure,
  envir = environment(),
  dir = get_mypath("data"))
#habitat_press
```

```{r}
test <- log_bm_net_group %>%
  filter(variable == "connectance") %>%
  left_join(habitat_pressure, by = "station")
test %>%
  pivot_longer(
    cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
    names_to = "evt_var", values_to = "value") %>%
ggplot(aes(y = bm_slope, x = value)) +
geom_point() +
facet_wrap(~evt_var, scales = "free_x")
```

```{r}
library(sf)
myload(region_polygon, envir = environment(), dir = get_mypath("data"))
myload(station_analysis,
  envir = environment(),
  dir = "~/Documents/post-these/mnhn/fishcom/data")

p <- ggplot() +
  geom_sf(data = st_geometry(region_polygon)) 
st_bm_slope <- station_analysis %>%
  rename(station = id) %>%
  left_join(select(test, station, bm_slope)) %>%
  filter(!is.na(bm_slope))
p + 
  geom_sf(data = st_bm_slope, aes(color = bm_slope)) +
  scale_color_viridis()
```
